---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MTLR
[![Build Status](https://travis-ci.org/haiderstats/MTLR.svg?branch=master)](https://travis-ci.org/haiderstats/MTLR)
[![codecov](https://codecov.io/gh/haiderstats/MTLR/branch/master/graphs/badge.svg)](https://codecov.io/gh/haiderstats/MTLR) 

The goal of `MTLR` is to provide an R implementation for [Multi-Task Logistic Regression](https://papers.nips.cc/paper/4210-learning-patient-specific-cancer-survival-distributions-as-a-sequence-of-dependent-regressors). In addition to supplying the model provided by [Yu et al.](https://papers.nips.cc/paper/4210-learning-patient-specific-cancer-survival-distributions-as-a-sequence-of-dependent-regressors) we have extended the model for left censoring, interval censoring, and a mixture of censoring types. Functionality includes training an MTLR model, predicting survival curves for new observations, and plotting these survival curves and feature weights estimated by MTLR.

## Installation

You can install the version from CRAN or the development version from GitHub:

```{r, eval = FALSE}
# CRAN:
install.packages("MTLR")

# GitHub:

# install.packages("devtools")
devtools::install_github("haiderstats/MTLR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
